An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-02 poly-embed-journal/poly-embed-journal.tex
response

\usetikzlibrary{calc}
\newcommand{\Comments}{0}
\newcommand{\CommentsR}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\reviewerresponse}[2]{\ifnum\CommentsR=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\reviewer}[1]{\reviewerresponse{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\begin{definition}[Separated Link]\label{def:sep-link}
  Let properties $\Gamma:\simplex\toto\reals^d$ and $\gamma:\simplex\toto\R$ be given.
  We say a link $\psi:\reals^d\to\R$
  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$, $p\in\simplex$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
  \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications, such as hinge loss for binary classification.}
  Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
  \raft{FYI, this def, along with Theorem~\ref{thm:discrete-loss-poly-embeddable} and Theorem~\ref{thm:calibrated-separated}, are referenced specifically from the top-k paper, so hopefully the numbers don't change by the time we post on arXiv}
\end{definition}

@@

@@

In previous work, we introduce and present some bounds for embedding dimension
based on optimality conditions \citep{finocchiaro2020embedding}\raft{Thoughts on using 1st person plural here for previous work?  It is the same authors, and same broader project... I think it's less awkward this way, but I'm okay with 3rd person too}\jessiet{So long as we're submitting to a single-blind venue, I'm fine with it.}.
We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these quantities may be the same for all discrete losses.
It is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
Moreover, beyond the fact that the embedding dimension upper bounds convex elicitation complexity, it remains to understand the relationship between these two quantities in dimensions greater than~$1$.

@@

\paragraph{Polyhedral vs.\ smooth surrogates}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
In practice, minimizing such surrogates often implicitly fits a model to the full conditional label distributions.
On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.
Even further, \citet{lapin2016loss} suggest that optimizing a nonsmooth loss that directly captures the target problem of interest, rather than a smooth one that implicitly fits to the full conditional label distributions, can improve performance in limited data settings.
We would like to verify this intuition, with specific cases or broad results comparing smooth and polyhedral losses.
  % \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
  % See references recommended by Peter Bartlett.}
%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.

>>>>

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\CommentsR}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\reviewerresponse}[2]{\ifnum\CommentsR=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\reviewer}[1]{\reviewerresponse{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\begin{definition}[Separated Link]\label{def:sep-link}
  Let properties $\Gamma:\simplex\toto\reals^d$ and $\gamma:\simplex\toto\R$ be given.
  We say a link $\psi:\reals^d\to\R$
  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$, $p\in\simplex$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
  \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications.  For example, taking hinge loss for binary classification, the sign link is 1-separated under the weak inequality, but only $(1-\delta)$-separated for $\delta > 0$ under the strict inequality.}
  Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
  \raft{FYI, this def, along with Theorem~\ref{thm:discrete-loss-poly-embeddable} and Theorem~\ref{thm:calibrated-separated}, are referenced specifically from the top-k paper, so hopefully the numbers don't change by the time we post on arXiv}
\end{definition}

@@

\raf{TODO: add paragraph on multiclass case, where $k=1$!}

@@

In previous work, we introduce and present some bounds for embedding dimension
based on optimality conditions \citep{finocchiaro2020embedding}.
We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these quantities may be the same for all discrete losses.
It is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
Moreover, beyond the fact that the embedding dimension upper bounds convex elicitation complexity, it remains to understand the relationship between these two quantities in dimensions greater than~$1$.

@@

\paragraph{Polyhedral vs.\ smooth surrogates}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
In practice, minimizing such surrogates often implicitly fits a model to the full conditional label distributions.
On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.%
\footnote{Polyhedral losses may be more challenging to optimize in some cases than smooth losses, so the prediction dimension may need to be much smaller, as in the BEP surrogate, until one sees a computational benefit.}
While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.
Even further, \citet{lapin2016loss} suggest that optimizing a nonsmooth loss that directly captures the target problem of interest, rather than a smooth one that implicitly fits to the full conditional label distributions, can improve performance in limited data settings.
We would like to verify this intuition, with specific cases or broad results comparing smooth and polyhedral losses.
  % \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
  % See references recommended by Peter Bartlett.}
%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
